Inference methods comparison for the simplified Naomi model using the Kolmogorov-Smirnov test statistic

### 2023-05-24 src/naomi-simple_ks/ks.Rmd
Clean up KS report

ks_df_out <- function(par) {
  to_ks_df(par = par, outputs = TRUE, id = mf_out_fine$id) %>%
  select(-par) %>%
  left_join(
    mf_out_fine %>%
      rename("full_id" = "id") %>%
      tibble::rowid_to_column("index") %>%
      mutate(index = as.numeric(index))
  )
}

```

@@

```{r}
ks_helper("beta", starts_with = TRUE)
```

@@

```{r}
ks_df_out(par = "rho_t1_out") %>%
  filter(!age_group %in% c("Y005_009", "Y010_014", "Y080_999")) %>%
  ks_plot(par = "lambda_t1_out", alpha = 0.2)
```

Filter out the age group 5-9, 10-14 and 80+ here becausethere are new new infections in those age groups, and the posterior samples from each method are exactly the same: in particular draws of identically zero.

```{r}
ks_lambda_t1_out %>%
  filter(ks == 0) %>%
  group_by(method) %>%
  summarise(n = n())

ks_lambda_t1_out %>%
  filter(ks == 0) %>%
  pull(age_group) %>%
  unique()
```

@@

saveRDS(ks_summary_out, "ks_summary_out.rds")

@@

```{r}
(ks_summary_out <- ks_summary %>%
  group_by(Type) %>%
  summarise(
    TMB = mean(`KS(TMB, tmbstan)`),
    aghq = mean(`KS(aghq, tmbstan)`),
    adam = mean(`KS(adam, tmbstan)`)
  )) %>%
  gt::gt()
```

@@

```{r}
ks_table(ks_summary, type = "Latent field")
```

@@

```{r}
ks_table(ks_summary, type = "Latent field")
```

>>>>

ks_df_out <- function(par) {
  to_ks_df(par = par, outputs = TRUE, id = mf_out_fine$id) %>%
  select(-par) %>%
  left_join(
    mf_out_fine %>%
      rename("full_id" = "id") %>%
      tibble::rowid_to_column("index") %>%
      mutate(index = as.numeric(index))
  )
}
```

@@

```{r}
ks_helper("beta", starts_with = TRUE)

#' Save off KS results for one parameter as example
saveRDS(
  to_ks_df(par = "beta_alpha", starts_with = TRUE),
  file = "beta_alpha.rds"
)
```

@@

```{r}
ks_df_out(par = "lambda_t1_out") %>%
  filter(!age_group %in% c("Y005_009", "Y010_014", "Y080_999")) %>%
  ks_plot(par = "lambda_t1_out", alpha = 0.2)
```

Filter out the age group 5-9, 10-14 and 80+ here because there are new new infections in those age groups, and the posterior samples from each method are exactly the same: in particular draws of identically zero.

```{r}
# ks_lambda_t1_out %>%
#   filter(ks == 0) %>%
#   group_by(method) %>%
#   summarise(n = n())
# 
# ks_lambda_t1_out %>%
#   filter(ks == 0) %>%
#   pull(age_group) %>%
#   unique()
```

@@

saveRDS(ks_summary, "ks_summary.rds")

@@

```{r}
ks_summary %>%
  group_by(Type) %>%
  summarise(
    TMB = mean(`KS(TMB, tmbstan)`),
    aghq = mean(`KS(aghq, tmbstan)`),
    adam = mean(`KS(adam, tmbstan)`)
  ) %>%
  gt::gt()
```

@@

```{r}
ks_summary %>%
  filter(Type == "Latent field") %>%
  group_by(Parameter) %>%
  summarise(
    `KS(TMB, tmbstan)` = mean(`KS(TMB, tmbstan)`),
    `KS(aghq, tmbstan)` = mean(`KS(aghq, tmbstan)`),
    `KS(adam, tmbstan)` = mean(`KS(adam, tmbstan)`)
  ) %>%
  ks_table()
```

@@

```{r}
# ks_summary %>%
#   filter(Type == "Hyper") %>%
#   group_by(Parameter) %>%
#   summarise(
#     `KS(TMB, tmbstan)` = mean(`KS(TMB, tmbstan)`),
#     `KS(aghq, tmbstan)` = mean(`KS(aghq, tmbstan)`),
#     `KS(adam, tmbstan)` = mean(`KS(adam, tmbstan)`)
#   ) %>%
#   ks_table()
```
